Figures

### 2019-08-07 figures/07_model-selection.Rmd
add forest models

```{r tn_fe, out.width="3.25in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
fit_tn         <- re_brms[[9]] # 5 is best tn model with random effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r re-comparison, fig.width=4}
# tp, tn
# ag, row_crop, pasture, corn, soybeans
re_global <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
re_global$term <- unlist(lapply(re_brms, 
                                function(x) get_re_text(as.character(x$formula)[1])))
re_global$response <- c(rep("tp", 5), rep("tn", 5))
re_global <- dplyr::filter(re_global, term != "rowvcropvpct")

>>>>

```{r tn_fe, out.width="3.25in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
fit_tn         <- re_brms[[11]] # 11 is best tn model with random effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r re-comparison, fig.width=4}
# tp, tn
# ag, row_crop, pasture, corn, soybeans
re_global <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
re_global$term <- unlist(lapply(re_brms, 
                                function(x) get_re_text(as.character(x$formula)[1])))
re_global$response <- c(rep("tp", 6), rep("tn", 6))
re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
